Constraints on Assembly Bias from Galaxy Clustering.

### 2016-06-08 ms.tex
Updated text with new figure of direct HODs, resolving #11

>>>>

%=-------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[width=8.0cm]{central_hod_comparison.pdf}
\includegraphics[width=8.5cm]{satellite_hod_comparison.pdf}
\caption{
We show the first moments of the central and satellite occupation distributions 
from the best-fit models to the $\magr<-20$ sample in the left and right 
panels, respectively. The green curve shows the HOD of our best-fit model 
that includes the effect of assembly bias; the red curve shows the HOD 
of the best-fit model in which assembly bias is assumed to be zero; 
the dashed black curve shows the best-fit HODs from \citet{zehavi_etal11}. 
The green error band around the decorated HOD results shows the variance 
in the HOD from randomly sampling one hundred points in parameter space 
with $\chi^{2}_{\rm model} - \chi^{2}_{\rm min} < 1.$
}
\label{fig:directhodcomparison}
\end{center}
\end{figure*}
%----------------------------------------------------------------------------------------------------
